### 2019-06-05 doc/appendix/appendixexemple.tex
added foot note
fixed footnotes
fixed appendix

@@

During this work, Stainless bumped the sbt plugin from version 0.13.17 to 1.2.8 and Scala from 2.11.12 to 2.12.8.
So this section might be out of date now.

@@

So the sbt plugin does not complain always but the JAR file did.
The open issue \mypound484 on GitHub might describe this error.

>>>>

\addcontentsline{toc}{chapter}{APPENDICES}

@@

During this work, Stainless bumped the sbt plugin from version 0.13.17 to 1.2.8 and now supports also Scala 2.12.8 and prevoiusly 2.11.12.
So this section might be out of date now.

@@

So the sbt plugin does not complain always but the JAR file did.
The open issue \mypound484 on GitHub\footnote{url{https://github.com/epfl-lara/stainless/issues/484}} might describe this error.
